\documentclass[conference]{IEEEtran}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[round]{natbib}

\usepackage{amsmath}
\usepackage[hyphens]{url}
\usepackage{xurl}
\providecommand{\harvardurl}[1]{\url{#1}}
\usepackage{etoolbox}
\AtBeginEnvironment{thebibliography}{\sloppy}
\usepackage{hyperref}
\newcommand{\BibTeX}{\textrm{B \kern -.05em \textsc{i \kern -.025em b} \kern -.08em
T \kern -.1667em \lower .7ex \hbox{E} \kern -.125emX}}
\begin{document}

    \title{Digital Twin Framework for Autonomous Drone Swarm Coordination in Maritime SAR Operations}

    \author{\IEEEauthorblockN{Nandakishore Vinayakrishnan}
    \IEEEauthorblockA{\textit{Department of Computer Science and Information Systems} \\
    \textit{University of Limerick}\\
    Limerick, Ireland \\
    https://orcid.org/0009-0009-7390-5955}}

    \maketitle

    \begin{abstract}
        Maritime Search and Rescue (MSAR) operations rely on effective coordination and operational readiness among several assets.
        This project proposes a modular Digital Twin framework to enable autonomous drone swarms to coordinate SAR missions in maritime environments.
        The framework seeks to integrate real-time sensor data, digital-physical system synchronization, and Human-in-the-Loop (HITL) interactions to enhance situational awareness and decision-making.
        A simulation-based approach will be employed to validate that framework, focusing on swarm coordination, Human-Computer Interaction principles, and overall situational awareness.
        This work seeks to address the critical gap between centralized SAR systems and decentralized autonomous operations, with the aim of improving response times and increasing readiness by enabling the utilization of more economic assets.
    \end{abstract}

    \begin{IEEEkeywords}
        Digital Twin, Autonomous Unmanned Aerial Vehicles (UAVs), Swarm Coordination, Maritime Search and Rescue, Human-in-the-Loop, Real-time Data Integration, Human-Computer Interaction, Cyber-Physical Systems, Real-time Simulation
    \end{IEEEkeywords}


    \section{Introduction}\label{sec:introduction}

    \subsection{Motivation}\label{subsec:motivation}
    Maritime accidents constitute time-critical humanitarian emergencies in which survival rates correlate directly with response times.

    Recent advances in autonomous Unmanned Aerial Vehicle (UAV) and Unmanned Surface Vessel (USV) technologies, combined with swarm intelligence, present transformative opportunities.
    Operating Unmanned Vehicles in Swarms allows for greater coordination, and increased redundancy in the face of potential communication and maintenance issues that may arise at sea.
    However, managing Drone Swarms at scale remains difficult due to the limited amount of certified human operators, and concerns about human cognitive load.

    Digital Twin (DT) Technology offers a promising framework for swarm coordination.
    By maintaining a synchronized virtual representation of physical Unmanned Vehicle swarms, DTs enable increased abstraction, easing cognitive loads on operators, in addition to potentially enabling predictive analysis, scenario-testing, and autonomous decision-making.

    Traditional SAR methods face substantial limitations, such as limited search coverage, difficulties in maintaining full readiness, high operational costs, extended response times, and coordination challenges in dynamic environments, as discussed in ~\cite{sar_challenges}.

    \subsection{Problem Statement}\label{subsec:problem-statement}
    Traditional MSAR operations suffer from several critical limitations.

    Human operators may experience increased cognitive overload during maritime deployments.
    In~\cite{riverine_MSAR_stress}, MSAR crew, in the context of riverine MSAR operations, tend to suffer marked increases in response time, and difficulties locating targets.
    The study found that MSAR crew reporting neither stress nor exertion located 78\% of deployed targets, while crew reporting both conditions located only 57\%.
    In addition, maintaining full readiness for larger, human-operated assets like vessels, helicopters and aircraft can be difficult if not economically impossible in some regions, leading to delays in response time due to poor maintenance, lack of fuel, etc.

    While drone solutions have been proposed and tested in real-life, like in ~\cite{multi-robot-team-MSAR}, many implementations do not use autonomous solutions.
    Instead, relying on a team of human operators to manage drones in a one-to-one fashion.
    When such solutions are scaled up, human operators can quickly reach cognitive overload, reducing response times.

    \subsection{Proposed Solution}\label{subsec:proposed-solution}
    This project proposes a Digital Twin Framework for Autonomous Drone Swarm Coordination with the intent of benefitting Maritime Search and Rescue operations.
    The framework seeks to integrate the Physical, Digital, and Service Layers of MSAR missions.

    It seeks to connect Autonomous Drones, usually equipped with sensors, life-saving equipment, GPS, and other communications modules, in a Physical Layer.
    These drones should be able to individually avoid obstacles, and generate their own paths when ground station connection is unavailable.

    In the swarm coordination layer, the swarm inputs the orders given from the user and calculates optimal search coverage paths.

    The swarm, and individual drones, are then represented through high-fidelity virtual replicas incorporating real-time state synchronization, which would become the framework's Digital Layer.

    Finally, the interface layer allows human-swarm communication, where the human inputs mission parameters and objectives, and supervises the drone swarm.
    The operator should also be able to intervene and direct individual drones at any time.

    In this manner, the framework intends to enable autonomous or semi-autonomous coordination of unmanned assets while maintaining global objectives, hence reducing dependency on centralized control, and improving the fault tolerance behind the systems that make up MSAR operations.

    \subsection{Research Objectives}\label{subsec:research-objectives}
    This project aims to achieve the following objectives:

    \begin{enumerate}
        \item Develop a comprehensive Digital Twin Framework integrating UAV swarm simulation with real-time coordination algorithms.
        \item Evaluate the practicality of implementing Distributed Consensus-Based Coordination protocols for error handling, and generating search patterns.
        \item Design adaptive mechanisms that automatically assign tasks depending on environmental conditions and mission objectives.
        \item Demonstrate improvement in helping reduce cognitive overload for human operators compared to traditional methods.
    \end{enumerate}

    \subsection{Report Organization}\label{subsec:report-organization}
    The remainder of this report is to be structured as follows:

    \begin{itemize}
        \item Section II - Background Research and Literature Review surrounding Digital Twins, UAV Swarms, and MSAR
        \item Section III - Methodology
        \item Section IV - Project Timeline and Constraints
        \item Section V - Conclusion
    \end{itemize}


    \section{Background and Literature Review}\label{sec:background-and-literature-review}

    \subsection{Applications of Unmanned Vehicles in Search and Rescue Operations}\label{subsec:uav-applications-in-search-and-rescue-operations}
    MSAR represents a time-critical, high-stakes application domain where Unmanned Vehicles have the potential to provide substantial advantages.
    \citet{waharte2010supporting} demonstrated that autonomous UAVs can significantly enhance Search and Rescue operations, albeit in a terrestrial context.
    The aforementioned research also provides an analysis of search algorithms, techniques by which UAVs can be arranged to provide maximum coverage.

    Search algorithms like greedy heuristics, potential-based heuristics, and Partially Observable Markov Decision Process (POMDP) approaches reduce victim detection time compared to random search approaches.

    ~\cite{messmer2024uav,UAV_USV_SAR} expanded this technology to practical MSAR implementations, developing a comprehensive software framework combining onboard UAV detection with ground-station processing to reduce operator strain.
    They addressed critical practical challenges like bandwidth restrictions, which are typical in MSAR operations in remote areas such as open ocean.
    Their findings emphasized that practical SAR systems must be able to balance bandwidth limitations with real-time processing requirements.
    This might require further technical advancements before it can be safely deployed in remote environments while still offering real-time data processing.

    ~\cite{YANG2025113488} proposes a dual-layer task planning framework integrating UAV search capabilities with human-crewed execution, in complex indoor environments.
    It employed Coverage Path Optimization based on Clustering(CPOC) for planning the routes of UAVs, and Dynamic Guided Rapidly-Exploring Random Tree (DG-RRT*) for human navigation.
    This approach reportedly achieved a 7.3\%-28.7\% decrease in the time taken to complete the rescue mission, compared to traditional algorithms for search and rescue typically employed.

    This research proves that human-drone collaboration could demonstrate gains in efficiency over purely human missions, at least in complex indoor environments.

    Finally, research exists proposing the design of an Autonomous Unmanned Vessel directly intended for MSAR missions, indicating that practical implementation is close, assuming questions around implementation and coordination are solved~\cite{AUV_Proposal}.

    \subsection{Autonomous Drone Swarm Coordination and Multi-Agent Systems}\label{subsec:autonomous-drone-swarm-coordination-and-multi-agent-systems}
    Multi-Agent Swarm Coordination is an extensively studied topic in the field of robotics, and distributed systems.
    Swarm coordination draws inspiration from biological systems, including insect colonies, fish schools, and bird flocks.
    Although intended more for Computer Animation, ~\cite{10.1145/37402.37406} helped inform the basis for most swarm coordination technology.

    The implementation of Swarm Coordination requires distributed algorithms that enable autonomous self-organization without centralized control failure points, to prevent issues like midair collisions and sensor overlap.
    Systems such as EN-MASCA, proposed by ~\cite{ENMASCA2025}, although designed for Durian Orchards, represent a real-world implementation of Autonomous Drone Swarm Coordination.
    The proposed system, named EN-MASCA, demonstrated the application of Reinforcement Learning approaches to optimize formations and obstacle avoidance.
    While Reinforcement Learning approaches enable adaptive formation control, they require substantial training resources, potentially increasing costs past traditional SAR assets.

    ~\cite{dev2025swarnraft} proposed another algorithm, called ``SwarmRaft'', utilized a consensus-based approach to collectively decide on the current state for real-time swarm coordination in GNSS-denied environments.
    By leveraging distributed consensus mechanisms, SwarmRaft allowed drones to handle the inevitable connection issues at sea, in addition to boosting redundancy when individual units experience sensor degradation or sensor loss.
    Positioning errors can rapidly deteriorate and add onto themselves if in a GNSS-denied environment, which necessitates using onboard multi-sensor fusion, perhaps spread across the drones, to establish a common ``source of truth'' from where they can self-organize.

    Across most literature, one of the primary motivators of creating Swarm Coordination mechanisms seems to be preventing collisions with both terrain and other drones.
    While this issue is partially mitigated when operating over open ocean, care still needs to be taken in avoiding waves, and other seaborne obstacles.

    \subsection{Human Factors in Supervisory Control of Autonomous Drone Swarms}\label{subsec:human-factors-in-supervisory-control-of-autonomous-drone-swarms}
    The central problem of supervising multiple autonomous systems boils down into becoming a question about human cognitive loads.

    In a discussion centered on Situation Awareness in the context of flight systems, ~\cite{situation_awareness} discussed that, counterintuitively, passively monitoring highly automated systems have the potential to increase mental workload rather than decrease it.
    The book argued that it allowed users (in this instance, Pilots), to abstract systems away in their minds without understanding how they work, making error detection difficult.
    Such a phenomenon can become devastating in high-stress environments, like in-flight emergencies or at sea.
    This necessitates increased attention to interface design to maintain what the book terms ``Situation Awareness'', the operator's comprehension of relevant factors, current status, and enough background information to detect and handle errors appropriately even when stressed.

    ~\cite{CUMMINGS2007339} conducted extensive research on operator workload limits in Human UAV supervision.
    Their findings will prove incredibly consequential to this project, as many of the insights achieved help provide an understanding of the average drone operator's capacity.
    Under low-workload conditions, the study proved that operators, regardless of the amount of automation, were able to be accurate and maintain full situational awareness.
    However, when under high-workload conditions, operators would adopt strategies like load-shedding, where they focus on a smaller set of drones than the ones provided, and would suffer inaccuracies as a result.
    The operators that did adopt load-shedding strategies still outperformed the ones that attempted to share their attention across all UAVs, but both categories still suffered losses in accuracy compared to low-workload situations.
    Finally, operators with almost-fully-automated UAVs tended to place unnecessary trust on the system, content to let the computer take care of mission-critical actions with no manual cross-checking, in a phenomenon known as ``Automation Bias''.

    ~\cite{wickens2011cognitive}, at the 16th International Symposium on Aviation Psychology, helped draw up a cognitive model of UAV control.
    It revealed that workload tends to ``spike'' right before, and during high-task phases of a mission.
    In the example used by the paper, operators experienced the most workload directly when they had to strike a given target.
    The report also directly corroborates many of the conclusions reached in Cummings' study.
    We can extrapolate this information to MSAR, and assume that an operator's workload is highest at the point of detection and active rescue.
    The model predicts the performance of multitasks based on resource allocation, and task priority.

    Overall, research indicates that operators of human-supervised swarms require highly specialized interfaces enabling them to perform the following:

    \begin{itemize}
        \item Define Task Priority
        \item Allocate Swarm subgroups to certain sets of subtasks
        \item Real-time Swarm Behavior Monitoring
        \item Explained, intuitive insight into System Decisions
        \item Instant intervention when necessary.
    \end{itemize}

    \subsection{Gaps and Research Opportunities}\label{subsec:gaps-and-research-opportunities}
    While substantial prior works exist that address features like Human-Computer Interaction principles in supervising autonomous systems, drone swarm coordination, and the applications of unmanned vehicles in MSAR operations, limited research integrates these domains.
    Due to this, there is a lack of research that addresses the specific challenges of single-operator-supervised Drone Swarms employed specifically for Maritime Search and Rescue.

    Few frameworks simultaneously integrate swarm autonomy, digital twin state management, and specific human-swarm interfaces optimized for MSAR missions.
    This forces potential research to make assumptions, extrapolating from existing data to draw conclusions, and even needing entirely new bodies of research to facilitate this.

    Most research into drone swarms and human factors assume high-bandwidth communication, which is usually impossible in MSAR scenarios.
    This necessitates intelligent information prioritization, fault-tolerant mechanisms, and helpful ways to fill in data gaps from inevitable connectivity issues.

    An important gap for the purposes of this project was also the lack of quantifiable measures of cognitive load during swarm supervision.
    Limited work establishes a concrete ratio of human-operator-to-drones, as such a measure would be difficult to maintain across several people with different management styles.
    There is also limited work validating the effectiveness of human-swarm interface design through objective metrics like NASA-TLX\@.

    The project seeks to address these gaps through an integrated framework combining proven techniques from each domain, optimized specifically for MSAR operations.


    \section{Methodology}\label{sec:methodology}

    \subsection{System Architectural Overview}\label{subsec:system-architectural-overview}
    The project seeks to propose a Digital Twin framework for Autonomous Drone Swarm Coordination that comprises 5 layers.

    \begin{enumerate}
        \item \textbf{Physical Layer:} This layer comprises physical drones equipped with comprehensive sensor and navigation suites, including cameras, LiDAR, GPS modules, and inertial measurement units (IMUs).

        \item \textbf{Individual Drone Autonomy Layer:} Each drone needs to be capable of autonomous global path calculation, rudimentary obstacle avoidance, and local state estimation.
        This can be achieved using algorithms like RRT* and Dynamic Window Approach-esque systems in combination with the system's on-board sensor suite.

        \item \textbf{Swarm-Level Coordination Layer:} This layer manages the collective behavior of the drone swarm.
        It seeks to employ distributed consensus algorithms, like SwarmRaft, to establish the current state while reducing reliance on remote/ground-station communication.
        Search area coverage can also be optimized at this layer, using techniques like Voronoi Tessellations to optimally divide the search area among individual drones.

        \item \textbf{Digital Twin \& Decision Support Layer:} This layer is designed to maintain a high-fidelity virtual simulation of a physical drone swarm.
        In this layer, predictive physics models could potentially be employed to detect anomalies, allowing alerts to be raised in critical situations.
        The Digital Twin could act as a decision-support system, providing enough information to human operators to allow them to make informed operational decisions.

        \item \textbf{Human-Swarm Interface Layer:} This layer focuses on the design of an intuitive interface that allows human operators to interact with and supervise the drone swarm in real-time.
        The interface could potentially provide a map-based visualization of drone positions, across an operational area.
        Using systems similar to the ones employed in glass cockpit-aircraft, the interface could provide alerts and general notifications based on priority.
        Finally, the interface must also allow operators to specify search areas, designate high-priority areas, and, in some cases, directly intervene in individual drone operations.
        Such an interface needs to be intuitive, to reduce cognitive load on operators.
    \end{enumerate}

    \subsection{Evaluation Methodology}\label{subsec:evaluation-methodology}

    \subsubsection{Workload Assessment}
    The primary metric used to evaluate the effectiveness of the proposed framework's cognitive load management would be the NASA-TLX workload assessment tool.

    NASA-TLX \citep{HART1988139} is a widely adopted instrument for assessing perceived workload across six dimensions:

    \begin{itemize}
        \item Mental Demand - How mentally demanding was the task?
        \item Physical Demand - How physically demanding was the task?
        \item Temporal Demand - How hurried or rushed was the pace of the task?
        \item Performance - How successful were you in accomplishing what you were asked to do?
        \item Effort - How hard did you have to work to accomplish your level of performance?
        \item Frustration Level - How insecure, discouraged, irritated, stressed, and annoyed were you?
    \end{itemize}

    Each subscale would be rated across 21 graduations, from ``Very Low'' to ``Very High''.
    Then, each dimension would be weighted based on pairwise comparisons to determine each dimension's importance to the overall workload.
    For instance, in the context of MSAR operations, Mental Demand and Temporal Demand may be weighted higher than Physical Demand.

    The overall workload score would then be calculated using the weighted average of each dimension's score.

    The framework aims to achieve a NASA-TLX score $\leq 60/100$, with the highest possible number of drones supervised by a single operator.

    \subsubsection{Operational Metrics}\label{subsubsec:operational-metrics}
    In addition to workload assessment, several operational metrics would be tracked to evaluate the effectiveness of the proposed framework.
    The primary operational metrics are as follows:

    \begin{itemize}
        \item \textbf{Search Coverage Efficiency} - Percentage of the designated search area covered by the drone swarm within a specific unit of time.
        \item \textbf{Target Detection Rate} - The number of targets detected divided by the total number of targets present in a given search area.
        \item \textbf{Completion Time} - The total time taken to complete an MSAR mission.
        \item \textbf{Operator Intervention Frequency} - The number of manual actions made per scenario
        \item \textbf{Error Response Time} - The time taken between the occurrence of an error, simulated or real, and its resolution
        \item \textbf{Misc. System Metrics} - Factors like latency, Uptime percentage, processing requirements.
    \end{itemize}

    \subsubsection{Validation Scenarios}\label{subsubsec:validation-scenarios}
    To validate the proposed framework, a series of simulation-based scenarios would be designed to mimic plausible scenarios during MSAR operations.
    These scenarios are intended to vary in complexity, environmental conditions, and the number of drones involved.

    The first scenario would involve a simple MSAR operation under nominal conditions, intended to work as a ``control'' scenario from where the basis of comparison can be drawn.

    In the next scenario, Wi-Fi communications would be progressively degraded, to force mesh networking and to test the swarm's fault tolerance.
    This scenario would act as a test for the interface and Digital Twin's ability to maintain situational awareness despite intermittent connectivity.
    An example for the connectivity degradation pattern could be simulating a 200ms latency, with a 5-10\% packet loss rate.

    Third, an emergency response scenario would be simulated, where some drones may suffer random malfunctions.
    The operator, or the system, if applicable, would then need to respond to these emergencies.
    This allows us to evaluate the system's error detection and handling capabilities, in addition to studying the operator's resilience in high-stress situations.

    Finally, the last scenario would involve an increased number of drones, with the aim of finding the ideal number of drones an operator can supervise without exceeding our maximum NASA-TLX workload score.


    \section{Project Timeline and Constraints}\label{sec:project-timeline-and-constraints}

    \subsection{Project Timeline}\label{subsec:project-timeline}

    \subsubsection{Week 1-4: Literature Review}\label{subsubsec:literature-review}
    The project commences with a comprehensive literature review encompassing Digital Twins, drone swarm coordination, and maritime SAR operations.
    This time will be used to define the use cases of the project and the system scope.

    \textbf{Key Deliverables}: Interim Report, Simulator Setup, Baseline Workload Assessment

    \subsubsection{Weeks 4-8: Architectural design of Twin}\label{subsubsec:architectural-design-of-twin}

    Define the module’s technical requirements, and architecture.
    Place effective foundations that can be worked on long-term.
    This is also where coupling schemes are decided on.

    \textbf{Key Deliverables}: Digital Twin architecture foundation, simulated outputs from physical infrastructure by creating sample API inputs

    \subsubsection{Weeks 8-12: Digital Twin Base Models \& Simulation Environment Setup}\label{subsubsec:digital-twin-base-models-&-simulation-environment-setup}

    Implement baseline swarm coordination schemes, and their virtual models.
    Create ``real'' (simulated) states that can be fed to the twin, which allows the twin to work on predicting simulations.

    Decide on physical real-world simulation, and integration strategies.
    Additionally, decide on how the Digital Twin can optimize future coordination, e.g.\ letting the twin optimize future trajectories, reassigning tasks, and error handling.

    \textbf{Key Deliverables}: User Interface, Sample API Input Handling, additional features as decided above.

    \subsubsection{Weeks 12-16: Integration and Stress Testing}\label{subsubsec:-integration-and-stress-testing}

    Decide on if integrating the Digital Twin model with a physical real-world example is feasible.
    Create a set of challenging maritime SAR “missions” to stress test the system.
    This must include aspects like dispersed targets, intermittent communication, and drone failures.

    \textbf{Key Deliverables}: Mission Simulation, Testing Framework, with multiple scenarios as lined out in Section~\ref{subsubsec:validation-scenarios}

    \subsubsection{Weeks 16-20: Refinement and Metrics}\label{subsubsec:refinement-and-metrics}

    Collect metrics like latency, and coverage time to compare “twin-assisted” simulated SAR missions vs.\ ``manual'' ones.
    These results will be analysed statistically in the report.

    \textbf{Key Deliverables}: Metric collection system, using metrics defined in Section~\ref{subsubsec:operational-metrics}, notes comparing standard MSAR missions to simulation.

    \subsubsection{Weeks 20-25: Write Paper}\label{subsubsec:write-paper}

    Compose chapters and refine notes taken into a proper report.
    Include an intro, related work, methodology, experiments, results, discussion, and conclusion.
    After writing the first draft, the paper must be revised and reviewed.
    Time can be taken to fix weak points in experiments and refine narrative.

    \textbf{Key Deliverables}: Final Year Project Report, prepare code for submission

    \subsection{Constraints}\label{subsec:constraints}

    \subsubsection{Technical Constraints}

    While not all MSAR operations happen over open ocean, this framework would seek to be able to handle open-ocean conditions.
    ~\cite{s21082848} states that, for Command and Control, ``a 200 kbps uplink data rate,a packet error rate of less than 0.1\%, and network latency less than 50 ms is required''.
    When attempting to use commercial LTE networks, the paper noted that the system suffered a 94ms delay for both uplink and downlink, on the ground.
    We can reasonably predict that these issues would only be exacerbated on open ocean.

    Another issue that may be encountered during deployment may be issues with onboard processing.
    The DJI Matrice 400, released by ~\cite{DJI_Matrice400_Specs}, a recently-released drone at the time of writing, despite being expensive, only has 8GB RAM, with 128GB of UFS storage, in addition to any extra SD cards inserted by the user.
    Since the performance is relatively limited, even in more expensive units, care needs to be taken to ensure onboard systems don't exceed a drone's computational limit.

    Finally, another technical constraint to be worked around is the performance of individual sensors.
    Sensor failure must be directly handled at all times during deployment, given varying levels of severity depending on failure.

    \subsubsection{Operational Constraints}

    Real-world deployment testing exceeds the scope of this project due to logistical constraints.
    In a real-world deployment, testing drones in maritime environments would encounter significant logistical issues, especially in failure conditions where drone recovery may be difficult.

    Regulatory agencies like EASA put forward specific restrictions on the use of drones in maritime and over-land conditions.
    Any Unmanned Aerial System heavier than 250g, as per ~\cite{open_category_easa}, requires specific certifications to operate.
    Due to this, it would be ideal to perform initial User tests with trained and certified operators, which may skew measurements away.

    \subsubsection{Ethical \& Safety Constraints}

    To protect critical infrastructure, protect national assets, and for safety reasons, a wide variety of places in countries are blocked off from Drone Access.
    While avoiding these areas can be easily enforced using onboard geo-awareness systems, care must be taken to ensure that the framework is fully legally compliant.
    For example, the User Interface must be able to clearly mark red-zones for movement and suggest alternate, safer paths should emergencies occur.

    All operational decisions must require human oversight and approval.
    Autonomous engagement should only occur when due to direct interaction from a human operator, and the system must be able to quickly follow human intervention.

    An important ethical constraint faced by this program would be creating a data processing workflow.
    Since drones would be equipped with sensor suites, any data saved from those sensors would fall under GDPR protection, in the EU\@.
    Since the framework has no use for recorded data, steps must be taken to transparently delete data after it is no longer relevant, in addition to anonymizing records of previous incidents.

    Maritime SAR, usually being a time-sensitive operation, requires extensive verification and failure detection.
    While a false positive may cause a distraction that may go on to be devastating for search efforts, a false negative can be more harmful.
    To mitigate this, human-operators must be involved in the loop, especially in cases where targets have been found.

    Finally, a significant aspect of this system will be ensuring it can be trusted by the average user.
    Disclaimers need to be made clearly stating that this system seeks to supplement MSAR assets, and cannot work as a replacement.
    In addition, it may be imperfect and subject to issues with detection, and that all decisions must be made with human-operator approval.


    \section{Conclusion}\label{sec:conclusion}

    This interim report presents the methodology and design framework for developing a digital twin system to enable effective human supervision of autonomous drone swarms in MSAR operations.

    An extensive review of several literary sources was conducted in this report, establishing a solid theoretical grounding across UAV swarms, Digital Twins, and human factors.
    This analysis has also revealed critical gaps in maritime-specific multi-agent supervision frameworks.

    A five-layer architecture has been proposed in this report, integrating swarm coordination, digital twin functionality, and human-swarm interfaces.
    Labour has been divided across each layer, clearly indicating the specific responsibilities of each layer.

    Finally, this report has also established comprehensive evaluation protocols combining system and human performance metrics, which are vital to ensuring the feasibility of this program.

    This report and the upcoming project can also act as the foundation for future research on this topic, such as real-world testing with human operators.

    \bibliographystyle{agsm}
    \bibliography{interim_report}

\end{document}
